Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-03-15 fertile.Rmd
changed examples to miceps

1. Use clear separation, labeling, and documentation.
2. Automate processes when possible.
3. Design the data analysis workflow as a sequence of small steps glued together, with outputs from one step serving as inputs into the next. [**MENTION THE UNIX PHILOSOPHY**]

@@

• A well-designed file structure:

@@

• Good documentation:

@@

• Reproducible file paths:

@@

• Randomness is accounted for:

@@

[** NOTE ABOUT TIDYVERSE STYLE AND WHY WE ADD THAT**]

@@

```{r, include = FALSE, message = FALSE}
readr::write_csv(mtcars, "~/Desktop/my_data.csv")
library(tidyverse)

```

```{r, message = FALSE}
file.exists("~/Desktop/my_data.csv")
library(fertile)
read_csv("~/Desktop/my_data.csv")
```

```{r}
read.table("~/Desktop/my_data.csv")
```

@@

```{r, message = FALSE}
library(tidyselect)
proj_check_some(".", contains("paths"))
```

@@

\tiny
```{r, message = FALSE}
proj_analyze(".")
```
\normalsize

@@

```{r, message = FALSE, results = "hide"}
library(purrr)
library(forcats)
library(fertile)
read.csv("mtcars.csv")
```

@@

is_data_file("~/Desktop/my_data.csv")
is_image_file("~/Desktop/my_data.csv")
```

@@

She has just finished a research project and is looking to submit her work to a journal. When researching the journal to which she is interested in submitting, she discovers that it has high standards for research reproducibility and a dedicated editor focusing on that aspect of submission. She goes online and finds the journal's guidelines for reproducibility. They are more complete than any guidelines to which she has previously been required to conform. In addition to notes about file paths and randomness, the journal requires a clean, well-organized folder structure, broken down by file category and stripped of files that do not serve a purpose. [**add something about build chain and readme to requirements**]

>>>>

1. Use clear separation, labeling, and documentation.
2. Automate processes when possible.
3. Design the data analysis workflow as a sequence of small steps glued together, with outputs from one step serving as inputs into the next. This is a common suggestion within the computing community, originating as part of the Unix philosophy (@unix).

@@

1. A well-designed file structure:

@@

2. Good documentation:

@@

3. Reproducible file paths:

@@

4. Randomness is accounted for:

@@

5. Code conforms to tidyverse style:

  - Although not discussed in any of the literature mentioned previously, we also believe **tidyverse** integration to be very important. Code conformation to **tidyverse** style helps ensure that analyses meeting **fertile**'s recommendations will be able to integrate seamlessly with packages from the **tidyverse**, an ever-expanding collection of packages designed to operate together with one another.

@@

```{r, message = FALSE}
library(fertile)
file.exists("project_miceps/mice.csv")
abs_path <- fs::path_abs("project_miceps/mice.csv")
read_csv(abs_path)
```

@@

```{r, message = FALSE}
library(tidyselect)
proj_check_some("project_miceps", contains("paths"))
```

@@

\tiny
```{r, message = FALSE}
proj_analyze("project_miceps")
```
\normalsize

@@

```{r, message = FALSE, results = "hide"}
library(purrr)
library(forcats)
library(fertile)
read.csv("project_miceps/mice.csv")
```

@@

is_data_file("project_miceps/mice.csv")
is_image_file("project_miceps/mice.csv")
is_image_file("project_miceps/proteins_v_time.png")
```

@@

She has just finished a research project and is looking to submit her work to a journal. When researching the journal to which she is interested in submitting, she discovers that it has high standards for research reproducibility and a dedicated editor focusing on that aspect of submission. She goes online and finds the journal's guidelines for reproducibility. They are more complete than any guidelines to which she has previously been required to conform. In addition to notes about file paths and randomness, the journal requires a clean, well-organized folder structure, broken down by file category and stripped of files that do not serve a purpose. In order to be approved, submissions must also have a clear build chain and an informative README file.
